ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura G\'ati).}

### 2018-07-31 Latex/Draft_Summer2018/Summer2018.tex
minor changes

Table \ref{table:estimated_parameters} shows results of Problem \ref{equation:min_prob_IRmatching}. The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$, while estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01$ and $0.9$ respectively.\footnote{Estimated parameter values are strongly robust to various alternative specifications. Using different empirical results, changing the initial calibration, the number of parameters matched or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These results convey a number of interesting messages regarding the fit of our two-sector model. Most importantly, the key question of our model was whether the presence of ICT shocks alone can account for the empirical responses we observe in data, or whether ICT diffusion plays a crucial role in this dynamics. This amounts to asking whether $\gamma = 0$ is supported by the data. Clearly, our estimate of $0.58$ rejects this hypothesis strongly. Thus, the data favor an interpretation of our model in which there are considerable spillovers to ICT capital. Accordingly, ICT shocks do not need to be large in magnitude to have sizable effects on TFP, GDP and consumption. This is indicated by the relatively small number we obtain for $\sigma^2_{\iota}$ of $0.01$. Confronted with data, the model is clearly telling a story in which there are small, but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run TFP growth because of large spillovers from ICT capital accumulation.
% does it make sense? I dont know what to say for sigmaiota and rhoiota...

Using the estimated parameter values in Table \ref{table:estimated_parameters}, Figure \ref{fig:IR_matching} displays empirical impulse responses along with theoretical ones. Our simple model is able to mimic empirical movements in TFP, ICT investment, consumption, and relative prices. In both the model and the data, a sector-specific technological shock $\zeta_t$ has a delayed positive effect on TFP which tends to last over the medium and long run. Moreover, in both cases, ICT investment has a large initial peak and then tends to remain persistently positive over the $40$-quarter horizon. In the model and the data, consumption responds positively on impact, reaches its peak after $4$ years and persistently remains positive. Finally, model-generated and empirical impulse responses of relative prices have a large and negative impact response which dies out in about $6$ years.

@@

\section{Estimated Parameters via IR Matching}

>>>>

Table \ref{table:estimated_parameters} in Appendix \ref{sec:appendix_table_IRmatching} shows results of Problem \ref{equation:min_prob_IRmatching}. The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$, while estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01$ and $0.9$ respectively.\footnote{Estimated parameter values are strongly robust to various alternative specifications. Using different empirical results, changing the initial calibration, the number of parameters matched or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These results convey a number of interesting messages regarding the fit of our two-sector model. Most importantly, the key question of our model was whether the presence of ICT shocks alone can account for the empirical responses we observe in data, or whether ICT diffusion plays a crucial role in this dynamics. This amounts to asking whether $\gamma = 0$ is supported by the data. Clearly, our estimate of $0.58$ rejects this hypothesis strongly. Thus, the data favor an interpretation of our model in which there are considerable spillovers to ICT capital. Accordingly, ICT shocks do not need to be large in magnitude to have sizable effects on TFP, GDP and consumption. This is indicated by the relatively small number we obtain for $\sigma^2_{\iota}$ of $0.01$. Confronted with data, the model is clearly telling a story in which there are small, but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run TFP growth because of large spillovers from ICT capital accumulation.
% does it make sense? I dont know what to say for sigmaiota and rhoiota...

Using the estimated parameter values in Table \ref{table:estimated_parameters}, Figure \ref{fig:IR_matching} in Appendix \ref{section:appendix_IR_matching} displays empirical impulse responses along with theoretical ones. Our simple model is able to mimic empirical movements in TFP, ICT investment, consumption, and relative prices. In both the model and the data, a sector-specific technological shock $\zeta_t$ has a delayed positive effect on TFP which tends to last over the medium and long run. Moreover, in both cases, ICT investment has a large initial peak and then tends to remain persistently positive over the $40$-quarter horizon. In the model and the data, consumption responds positively on impact, reaches its peak after $4$ years and persistently remains positive. Finally, model-generated and empirical impulse responses of relative prices have a large and negative impact response which dies out in about $6$ years.

@@

\section{Estimated Parameters via IR Matching}\label{sec:appendix_table_IRmatching}
